Finch: Sparse and Structured Array Programming with Control Flow

### 2024-04-01 sections/eval.tex
add intro text to evaluation.

>>>>

We evaluate Finch on a broad set of applications to showcase it's efficiency,
flexibility, and expressibility. All of our implementations highlight the
benefits of data structure and algorithm co-design.  Our implementation of
sparse-sparse-matrix multiply (SpGEMM) translates classical lessons from sparse
performance engineering into the language of Finch, using temporaries and
randomly-accessible workspace formats to efficiently implement the three main
approaches. Our study of sparse-matrix-dense-vector multiply (SpMV) highlights
the benefits of precise structural specialization. Our studies of image
morphology and graph applications show how Finch's programming model can express more complex
real-world kernels. Finally, we explain
how flexible operators, formats, and indexing expressions in Finch have
supported a flexible implementation of the Python Array API, supporting fused exection.
